Type Refinements for the Working Class

### 2015-11-22 paper.tex
wording

Then, we say that $\phi$ \emph{globally refines} $\tau$ (written
$\GRefines{\phi}{\tau}$) when we have $\Refines{\cdot}{\phi}{\tau}$.
Furthermore, when $\Refines{\Upsilon}{\phi}{\tau}$, for any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
we can define a new refinement $\phi\rho$ such that
$\Refines{\Upsilon'}{\phi\rho}{\tau}$ in the obvious way.

@@

In this section we generalize Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished
copresheaf $\Of{\CanOperators}{\Sets^{\SCtx\times\Discrete{\Arities}}}$ of
\emph{canonical} operators such that $\IsSubsetEq{\CanOperators}{\Operators}$.
For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define the
covariant presheaves on $\SCtx\times\Ctx$ of open expressions, open values, and open bound terms
as follows:
\begin{align*}
  \ADefine{\Exprs_\tau(\Upsilon\parallel\Gamma)}{
    \MkSet{M \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\Gamma}{M}{\tau}}
  }\\
  \ADefine{\Values_\tau(\Upsilon\parallel\Gamma)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon\parallel\Gamma)\land \exists a. \CanOperators\Pair{\Upsilon}{a}\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon\parallel\Gamma)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\Gamma}{E}{v}}
  }
\end{align*}

>>>>

Then, we say that $\phi$ \emph{globally refines} $\tau$ (written
$\GRefines{\phi}{\tau}$) when we have $\Refines{\cdot}{\phi}{\tau}$.
Furthermore, when $\Refines{\Upsilon}{\phi}{\tau}$, for any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
we can clearly define a new refinement $\Refines{\Upsilon'}{\phi\rho}{\tau}$.

@@

In this section we generalize Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished
presheaf $\Of{\CanOperators}{\Sets^{\SCtx\times\Discrete{\Arities}}}$ of
\emph{canonical} operators such that $\IsSubsetEq{\CanOperators}{\Operators}$.
For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define the
covariant presheaves on $\SCtx\times\Ctx$ of open expressions, open values, and open bound terms
as follows:
\begin{align*}
  \ADefine{\Exprs_\tau(\Upsilon\parallel\Gamma)}{
    \MkSet{M \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\Gamma}{M}{\tau}}
  }\\
  \ADefine{\Values_\tau(\Upsilon\parallel\Gamma)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon\parallel\Gamma)\land \exists a. \CanOperators\Pair{\Upsilon}{a}\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon\parallel\Gamma)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\Gamma}{E}{v}}
  }
\end{align*}
